---
title: "E-commerce Sentiment Analysis Showcase"
output: 
  html_document:
    theme: cosmo
    toc: true
    toc_float: true
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(ggplot2)
library(dplyr)
library(tidyr)
library(wordcloud)
library(plotly)
library(tidytext)
library(textdata)
library(RColorBrewer)
```

# Project Overview

This project analyzes sentiment in e-commerce product reviews to understand customer satisfaction and product performance. The analysis provides valuable insights into customer feedback and helps identify areas for improvement.

## Key Features

- Sentiment analysis of product reviews
- Visualization of sentiment distribution
- Word cloud analysis of common terms
- Interactive plots for better data exploration

## Data Analysis

```{r load-data}
# Load and prepare the data
data <- read.csv("Dataset.csv")

# Preprocess the CustomerReviewContent column
reviews <- data %>%
  select(CustomerReviewContent) %>%
  filter(!is.na(CustomerReviewContent)) %>%
  mutate(CustomerReviewContent = tolower(CustomerReviewContent)) %>%
  mutate(CustomerReviewContent = gsub("[[:punct:]]", " ", CustomerReviewContent)) %>%
  mutate(CustomerReviewContent = gsub("[[:digit:]]", " ", CustomerReviewContent))

# Tokenize the text into individual words
reviews_tokenized <- reviews %>%
  unnest_tokens(word, CustomerReviewContent)

# Use the Bing sentiment lexicon
bing_sentiments <- get_sentiments("bing")

# Join with the tokenized dataset to get sentiment scores
sentiment_scores <- reviews_tokenized %>%
  inner_join(bing_sentiments, by = "word") %>%
  count(sentiment, sort = TRUE)
```

### Sentiment Distribution

```{r sentiment-distribution}
# Create a sentiment distribution plot
sentiment_plot <- ggplot(sentiment_scores, aes(x = sentiment, y = n, fill = sentiment)) +
  geom_bar(stat = "identity") +
  labs(title = "Sentiment Distribution", x = "Sentiment", y = "Count") +
  theme_minimal() +
  scale_fill_brewer(palette = "Set2")

ggplotly(sentiment_plot)
```

### Word Cloud Analysis

```{r wordcloud}
# Generate word cloud from review text
wordcloud_data <- reviews_tokenized %>%
  count(word, sort = TRUE) %>%
  anti_join(stop_words)

wordcloud(words = wordcloud_data$word,
          freq = wordcloud_data$n,
          max.words = 100,
          colors = brewer.pal(8, "Dark2"))
```

## Interactive Visualizations

```{r interactive-viz}
# Calculate sentiment score for each review
review_sentiments <- reviews_tokenized %>%
  inner_join(bing_sentiments, by = "word") %>%
  group_by(CustomerReviewContent) %>%
  summarise(sentiment_score = sum(ifelse(sentiment == "positive", 1, -1))) %>%
  arrange(desc(sentiment_score))

# Create an interactive histogram of sentiment scores
plot_ly(data = review_sentiments,
        x = ~sentiment_score,
        type = "histogram",
        marker = list(color = "steelblue"),
        opacity = 0.7) %>%
  layout(title = "Distribution of Sentiment Scores",
         xaxis = list(title = "Sentiment Score"),
         yaxis = list(title = "Frequency"))
```

## Key Findings

1. **Sentiment Distribution**: The analysis reveals the overall distribution of positive and negative sentiments in the reviews using the Bing sentiment lexicon.

2. **Common Themes**: Through word cloud analysis, we can identify the most frequently mentioned terms in customer reviews, excluding common stop words.

3. **Sentiment Score Distribution**: The interactive visualization shows the distribution of sentiment scores across all reviews, helping identify the overall sentiment trend.

## How to Use This Project

1. Clone the repository
2. Install required R packages
3. Run the analysis script
4. Explore the visualizations and insights

## Technical Details

The project uses the following R packages:
- ggplot2 for static visualizations
- plotly for interactive plots
- wordcloud for text analysis
- tidytext for text processing and sentiment analysis
- dplyr and tidyr for data manipulation

## Future Improvements

- Add more advanced NLP techniques
- Implement real-time sentiment analysis
- Create a web interface for interactive analysis
- Add support for multiple languages
- Incorporate topic modeling for better theme identification

---

*This showcase page is automatically deployed using GitHub Actions whenever changes are pushed to the main branch.* 