---
title: "E-commerce Sentiment Analysis Showcase"
output: 
  html_document:
    theme: cosmo
    toc: true
    toc_float: true
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(ggplot2)
library(dplyr)
library(tidyr)
library(wordcloud)
library(plotly)
```

# Project Overview

This project analyzes sentiment in e-commerce product reviews to understand customer satisfaction and product performance. The analysis provides valuable insights into customer feedback and helps identify areas for improvement.

## Key Features

- Sentiment analysis of product reviews
- Visualization of sentiment distribution
- Word cloud analysis of common terms
- Interactive plots for better data exploration

## Data Analysis

```{r load-data}
# Load and prepare the data
data <- read.csv("Dataset.csv")
```

### Sentiment Distribution

```{r sentiment-distribution}
# Create a sentiment distribution plot
sentiment_plot <- ggplot(data, aes(x = sentiment)) +
  geom_bar(fill = "steelblue") +
  theme_minimal() +
  labs(title = "Distribution of Sentiment Scores",
       x = "Sentiment",
       y = "Count")

ggplotly(sentiment_plot)
```

### Word Cloud Analysis

```{r wordcloud}
# Generate word cloud from review text
wordcloud_data <- data %>%
  unnest_tokens(word, review_text) %>%
  count(word, sort = TRUE)

wordcloud(words = wordcloud_data$word,
          freq = wordcloud_data$n,
          max.words = 100,
          colors = brewer.pal(8, "Dark2"))
```

## Interactive Visualizations

```{r interactive-viz}
# Create an interactive scatter plot
plot_ly(data = data,
        x = ~rating,
        y = ~sentiment_score,
        type = "scatter",
        mode = "markers",
        marker = list(size = 10, opacity = 0.5),
        text = ~paste("Review:", review_text)) %>%
  layout(title = "Rating vs Sentiment Score",
         xaxis = list(title = "Rating"),
         yaxis = list(title = "Sentiment Score"))
```

## Key Findings

1. **Sentiment Distribution**: The analysis reveals the overall distribution of positive, negative, and neutral sentiments in the reviews.

2. **Common Themes**: Through word cloud analysis, we can identify the most frequently mentioned terms in customer reviews.

3. **Rating-Sentiment Correlation**: The interactive visualization shows the relationship between numerical ratings and sentiment scores.

## How to Use This Project

1. Clone the repository
2. Install required R packages
3. Run the analysis script
4. Explore the visualizations and insights

## Technical Details

The project uses the following R packages:
- ggplot2 for static visualizations
- plotly for interactive plots
- wordcloud for text analysis
- dplyr and tidyr for data manipulation

## Future Improvements

- Add more advanced NLP techniques
- Implement real-time sentiment analysis
- Create a web interface for interactive analysis
- Add support for multiple languages

---

*This showcase page is automatically deployed using GitHub Actions whenever changes are pushed to the main branch.* 